\documentclass[10pt,conference]{IEEEtran}

\usepackage{booktabs}
\usepackage{cite}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdfauthor={Anonymous Authors},
  pdftitle={MemorixBench-Transfer: A Fail-Closed Evaluation Design for Fresh-Agent Project Memory}
}

\newcommand{\memorix}{\textsc{Memorix}}
\newcommand{\bench}{\textsc{MemorixBench-Transfer}}

\title{\bench: A Fail-Closed Evaluation Design for Fresh-Agent Project Memory}
\author{Anonymous Authors}

\begin{document}
\maketitle

\begin{abstract}
Coding agents increasingly carry project memory across sessions, but a strong
fresh agent can often recover the needed state from current code and tests.
This makes a useful question conditional: when does predecessor evidence help a
new agent complete a later engineering task, and when does it only add stale
context or cost? We present \bench, a fail-closed evaluation design for this
question. It holds the evolved repository, ordinary tools, and bounded evidence
budget fixed while varying only the memory mechanism. The design separates an
equal-evidence canonical retrieval comparison from native product behavior,
records freshness and stale-claim risks, and reserves private-oracle claims for
isolated execution. A public reproducibility study covers twelve frozen Python,
TypeScript, and Go transfer fixtures. Its 144-run Qwen cohort is inconclusive
(+2.8 points for canonical \memorix{} over no memory; 95\% interval $[-8.3,
16.7]$), while a frozen 72-run DeepSeek replication reaches ceiling success for
both conditions and exposes context-cost overhead. These results are initial
boundary evidence, not a general effectiveness claim. The contribution is an
executable evaluation discipline that prevents small public diagnostics from
being misreported as proof that more memory is better.
\end{abstract}

\begin{IEEEkeywords}
agent memory, coding agents, evaluation, reproducibility, software engineering
\end{IEEEkeywords}

\section{Motivation}

Agent-memory systems are often evaluated by recall or preference-style tasks.
Those measurements matter, but they do not answer whether retained project
evidence changes a later coding agent's tested patch. The distinction becomes
more important as models improve: a capable fresh agent can inspect the current
repository, search source, and run focused tests without any predecessor
context. Injecting a long summary can then consume budget, delay useful work,
or promote an outdated assumption.

Existing memory evaluations cover conversational updates and abstention~\cite{wu2024longmemeval},
incremental multi-turn memory abilities~\cite{hu2025memoryagentbench}, and
interdependent agentic tasks~\cite{he2026memoryarena}; workflow-memory work
also induces reusable routines outside coding~\cite{wang2024agentworkflowmemory}. Dynamic-environment and
long-horizon coding benchmarks further show that evolving state is not new by
itself~\cite{xu2026evoarena,le2025sweevo,jin2026chainswe}. \textsc{MemorixBench-Transfer} focuses on a
narrower intervention: after a controlled repository evolution, can bounded,
freshness-aware predecessor evidence help a \emph{fresh} agent, relative to an
equally capable agent that sees the same current code?

This paper makes three contributions. First, it defines a causal comparison that
does not weaken the no-memory control. Second, it ships an executable public
study path with fail-closed receipts and a deliberately conservative analysis.
Third, it makes the evidence boundary explicit: public fixtures establish
reproducibility observations, while private-oracle effectiveness claims require
separate admission and isolation gates.

\section{Fresh-Agent Transfer Design}

A case consists of a precursor engineering session, a controlled repository
transition, and a later transfer task. The transfer agent receives the same
evolved checkout, editable source roots, current-code inspection tools,
verification commands, timeout, and actual model route in every condition. The
only intended difference is predecessor evidence and the mechanism that serves
it. The no-memory condition therefore remains free to read, search, edit, and
test the current project; it is not a deliberately weakened baseline.

\begin{figure*}[t]
\centering
\small
\begin{tabular}{@{}p{0.28\textwidth}c p{0.28\textwidth}c p{0.28\textwidth}@{}}
\toprule
\centering{}Precursor evidence & & \centering{}Shared transfer state & & \centering{}Evidence boundary \tabularnewline%
\midrule
\centering{}Durable decision plus potentially stale trace & $\longrightarrow$ & \centering{}Same evolved repository and ordinary tools; only bounded predecessor evidence changes & $\longrightarrow$ & \centering{}Public verifier now; private oracle only after isolation gates \tabularnewline%
\bottomrule
\end{tabular}
\caption{The intervention is predecessor evidence, not access to current code.
The transition snapshot and ordinary coding capability remain shared across
conditions.}\label{fig:transfer-boundary}
\end{figure*}

\begin{table}[t]
\caption{Canonical comparison surface. Every condition receives the same
transfer checkout and ordinary coding tools.}\label{tab:conditions}
\centering
\begin{tabular}{p{0.22\columnwidth}p{0.68\columnwidth}}
\toprule
Condition & Predecessor input before the transfer task \\
\midrule
No memory & None; current source and tests only \\
Raw replay & Bounded suffix of the normalized precursor trace \\
Canonical memory & Same bounded trace, formed and retrieved through a pinned adapter \\
Native product & Optional, one-call project-memory surface; reported separately \\
\bottomrule
\end{tabular}
\end{table}

The canonical surface gives comparable providers the same normalized precursor
trace and context ceiling. It supports a fair retrieval question, not a claim
that all products share the same native ingestion path. Native \memorix{}
behavior is consequently a separate product surface: the agent may choose one
bounded read, and its call count and served context are recorded instead of
being silently pooled with forced retrieval.

\subsection{Fail-Closed Rejection Rules}

The comparison is useful only when ordinary coding capability remains matched.
\bench{} therefore rejects, rather than scores, a row when a condition loses a
current-code tool, a transfer workspace differs from its registered snapshot,
the provider route is mixed or unreported, a case/oracle definition drifts, or
the planned matrix has a missing or duplicate row. A broken memory adapter is
an infrastructure failure rather than a zero. These checks make several common
shortcuts unreportable: hiding tests from no memory, treating a native hook
write path as equivalent to another system's replay input, or pooling different
actual models to make a small result table look larger.

\begin{table}[t]
\caption{Examples of evidence failures and the required handling.}\label{tab:rejections}
\centering
\begin{tabular}{@{}p{0.31\columnwidth}p{0.58\columnwidth}@{}}
\toprule
Observed failure & Required handling \\
\midrule
No-memory loses ordinary source or test access & Invalidate the matched run \\
Mixed or missing actual-model telemetry & Exclude the cohort from confirmatory inference \\
Public issue/patch supplies an answer & Retain only as source provenance \\
Native ingestion differs across systems & Report as a separate product surface \\
\bottomrule
\end{tabular}
\end{table}

Each run begins from a fresh materialized transfer workspace. The harness
removes previous Git history, rejects filesystem residue, and uses disposable
local home/cache directories; controlled Claude runs also disable session
persistence. This controls harness-visible cross-run state, not opaque
provider-side state or pretraining exposure. Public repository history is used
only as provenance because public tasks and solutions can contaminate model
evaluation~\cite{openai2026swebench}. A private transition, oracle, and raw
precursor event are never released to a public worker.

\subsection{Outcome and Analysis Contract}

Patch correctness is the primary outcome. A run passes only when the registered
transfer verifier accepts the sealed patch after the agent exits; a model's
explanation, a self-reported completion message, or a favorable memory lookup
cannot substitute for that verifier. The same verifier is used for every
condition in a case. Efficiency and freshness behavior are reported beside, but
never folded into, correctness. This distinction matters because a memory
mechanism can add useful evidence while still increasing provider token use or
wall-clock time, and because a fluent but stale explanation is not a correct
patch.

\begin{table}[t]
\caption{Outcome families are deliberately not interchangeable.}\label{tab:outcomes}
\centering
\begin{tabular}{@{}p{0.28\columnwidth}p{0.61\columnwidth}@{}}
\toprule
Outcome family & Measurement and interpretation \\
\midrule
Patch correctness & Registered deterministic transfer verifier after agent exit \\
Resource cost & Provider-reported input/output tokens, cost, wall time, and tool calls; descriptive unless preregistered \\
Freshness behavior & Blinded stale-conflict action only when a private label packet exists \\
Operational integrity & Route, workspace, formation, patch, and verifier receipts; failure invalidates a row \\
\bottomrule
\end{tabular}
\end{table}

For a matched treatment-control pair, the public analysis first averages fixed
repetitions within a case and then compares the resulting case-level outcomes.
This makes the case, rather than a retry, the unit of inference. A bootstrap
interval and a paired sign-flip statistic summarize the primary difference;
they are descriptive for the present public cohort. The analysis refuses to
silently repair a partially observed matrix. Missing rows, duplicate rows,
definition-hash drift, or an actual-model mismatch invalidate the aggregate
instead of being imputed as failures or dropped after inspection. The same
policy prevents pseudo-replication: repeating one easy fixture does not create
many independent engineering tasks.

The protocol also distinguishes a failed task from a failed experiment. A
verified patch that misses its task under a valid route is an observed task
failure. A timeout may be an observed outcome when the environment and route
receipts are intact. By contrast, an adapter crash, an unbound model route, a
leaked prior workspace, or a verifier that differs across conditions is an
infrastructure failure. It is surfaced with its receipt and removed from the
comparison; assigning it a zero to one condition would create a spurious memory
effect.

\section{Initial Public Reproducibility Study}

We froze a public transfer cohort of twelve local fixtures spanning Python,
TypeScript, and Go. It contains four predecessor-policy transfers, four
current-source-sufficient controls, and four stale or distracting-memory cases.
The first cohort used four conditions and three fixed repetitions (144 rows).
The registered primary contrast was canonical \memorix{} versus no memory; all
conditions used one provider-reported model and one bounded tool policy.

\begin{table}[t]
\caption{Frozen public cohorts. Repetitions are collapsed within each of twelve
case clusters before inference.}\label{tab:public-results}
\centering
\begin{tabular}{@{}p{0.17\columnwidth}p{0.16\columnwidth}p{0.56\columnwidth}@{}}
\toprule
Cohort & Valid rows & Descriptive observation \\
\midrule
Qwen & 144 & Canonical Memorix 35/36 vs.\ no memory 34/36; +2.8 points, 95\% interval $[-8.3,16.7]$, sign-flip $p=1.0$ \\
DeepSeek & 72 & Both canonical \memorix{} and no memory 36/36; canonical \memorix{} used about 2,206 more input tokens per case cluster \\
\bottomrule
\end{tabular}
\end{table}

The public results are intentionally mixed. The Qwen interval includes a
meaningful advantage and disadvantage, so it does not support a stable success
claim. The DeepSeek replication has no accuracy headroom on these fully public
fixtures and instead reveals a context-cost boundary. With only twelve
independent clusters, neither cohort is sensitive to modest effects. These are
useful negative constraints on product design: memory should earn its context
cost on a real dependency rather than be injected merely because a prior
session exists.

The study does not report stale-conflict action labels because it has no public
blinded-label packet, and it does not report a native-MCP outcome comparison;
the current native hook path is integration evidence only. Missing measurements
remain missing, never zero. Likewise, public fixtures cannot establish that a
task was unseen in pretraining, that a private oracle is secure, or that the
observations generalize across repositories and agent clients.

\subsection{Evidence Tiers}

The artifact separates three claims that are often collapsed. Deterministic
retrieval tests can show that an adapter forms and retrieves bounded evidence.
The public cohort can show that a fixed implementation and its mixed outcomes
are reproducible. Neither can establish a private-oracle engineering effect.
That final claim requires newly authored transitions, a private controller, and
independent execution evidence. This tiering is deliberately asymmetric: a
failure at a higher tier cannot be repaired by adding more public fixture runs.

\section{Artifact Contract}

The implementation is an artifact contract, not merely a prose protocol. Each
run binds a case-definition hash, clean transfer-tree identity, prompt hash,
ordinary-tool policy, formation receipt, actual-model telemetry, sealed patch,
and verifier receipt. The public analysis rejects a matrix with missing,
duplicate, mixed-model, or definition-drift rows before aggregate statistics
are produced. Repetitions are collapsed inside a case cluster; they characterize
stability rather than being counted as independent engineering problems.

\begin{table}[t]
\caption{Artifact layers and their enforced invariant.}\label{tab:artifact-contract}
\centering
\begin{tabular}{@{}p{0.25\columnwidth}p{0.64\columnwidth}@{}}
\toprule
Layer & Enforced invariant \\
\midrule
Case registry & Immutable case and oracle-definition commitments \\
Formation adapter & Bounded predecessor input with a provider-specific receipt \\
Run record & Clean start state, route/tool policy, patch, and verifier binding \\
Analysis manifest & Predeclared condition pairs and complete row matrix \\
Public release & Allowlisted files, credential/path scan, materialized self-test \\
\bottomrule
\end{tabular}
\end{table}

The release builder materializes only allowlisted public source, fixture, and
aggregate-result files into a fresh tree, scans for credential-like material
and host-specific paths, and reruns the public tests there. Raw client events,
private overlays, hidden verifier output, and local model settings remain
outside that tree. This lets a reviewer reproduce the bounded public study
without mistaking its sanitized inputs for a private-oracle benchmark.

\section{Threats to Validity and Scope}

The central internal-validity risk is unequal ordinary capability. A memory
condition that receives a useful shell command, a hidden test, a different
timeout, or a pre-warmed project checkout is not measuring predecessor evidence
alone. \textsc{MemorixBench-Transfer} addresses only harness-visible inequivalence: it commits the
transfer tree, tool policy, prompt, model-route receipt, and verifier. It cannot
observe an inference provider's private cache, hidden routing decision, or
pretraining exposure. The reported model name is consequently an attested local
observation, not proof of a completely isolated model state.

The main construct-validity risk is conflating a canonical comparison with
native product experience. Canonical adapters normalize the precursor trace and
rendered context budget so that systems can be compared without rewarding an
unrelated ingestion interface. That deliberately strips away some product
features. Native \memorix{} uses an agent-facing project-context call and may
include freshness, semantic-code, knowledge, and workflow evidence; it is
useful as a product diagnostic, but it is not pooled with a forced canonical
block or presented as a head-to-head native benchmark against products with
different interfaces. The current native hook implementation has passed
integration checks only, not an outcome study.

External validity is intentionally narrow. The public cohort has twelve
fixtures and two observed provider routes, and both public task sources are
visible enough that they cannot settle contamination or generalization. Its
ceiling DeepSeek result is informative precisely because it shows a strong
current-code agent may not need memory on simple public tasks. It does not show
that memory is useless on difficult, private, cross-session work. Conversely,
the small positive Qwen point estimate does not establish a general benefit.
The appropriate conclusion is conditional: memory needs a verified dependency
that current code alone does not cheaply resolve, and the study must retain a
strong no-memory control to demonstrate that dependency.

Finally, the artifact is not a claim that every software-engineering outcome
can be reduced to a deterministic checker. A private behavioral oracle can
supplement tests when design ownership matters, but it must be held by an
isolated controller and never revealed in the transfer prompt. The public
release deliberately withholds that layer. This reduces what can be claimed
today, while preserving a path to a stronger future study without leaking the
answer into the agent's context.

\section{Future Plans}

The next stage turns the design into a confirmatory engineering study without
reusing public issue/patch pairs as answers. Each real-repository lead requires
a newly authored post-snapshot transition, a private behavioral oracle, two
independent human admission reviews, and at least two precursor traces. A
separate worker, model-relay, and runtime-manager evidence chain must bind one
actual model, the sealed patch, and a KVM-backed controller/subject boundary.
The analysis plan and power envelope will be frozen before outcome labels are
read. These gates are deliberately stricter than the public study; absent gates
are a reason to withhold an effectiveness claim, not to relabel a local smoke
as evidence.

\subsection{Confirmatory Execution Sequence}

The first gate is case authoring and admission. A candidate begins as a source
lead, not as an outcome. The case author creates a new post-snapshot transition
and commits its task, reference repair, and behavioral oracle before any model
run. Independent reviewers inspect a hash-bound admission record rather than
the hidden answer. They must reject a lead if the current snapshot already
makes the transfer task trivial, if public history exposes the intended repair,
or if predecessor evidence is not plausibly necessary. This gate is costly, but
it prevents a memory study from selecting only cases where a remembered public
patch is the answer.

The second gate is isolated execution. The controller owns the private
transition and oracle; the worker owns only the evolved transfer checkout,
bounded condition input, and ordinary coding tools. A runtime manager seals
the patch before validation. A route receipt must bind one actual model for a
cohort, and the worker/controller boundary must be independently auditable.
The point is not to claim perfect epistemic isolation. It is to make every
remaining uncertainty named, bounded, and symmetric across conditions.

The third gate is analysis and replication. A frozen plan names the primary
comparison, required case clusters, missing-pair policy, and resource outcomes
before validators reveal outcome labels. An independent execution cohort then
repeats the full pathway with a second model route or agent client. Only a
consistent result on admitted private cases can support an effectiveness claim;
a result that appears only in a native product diagnostic can support product
engineering, not a cross-system causal conclusion.

\begin{table}[t]
\caption{Confirmatory gates are claim gates, not administrative checks.}\label{tab:confirmatory-gates}
\centering
\begin{tabular}{@{}p{0.26\columnwidth}p{0.61\columnwidth}@{}}
\toprule
Gate & What it permits, and what it still does not prove \\
\midrule
Private case admission & A dependency-bearing trial; not absence of all model contamination \\
Worker/controller isolation & A sealed outcome check; not proof about opaque provider state \\
Frozen paired analysis & A cohort-level effect estimate; not broad cross-project generalization \\
Independent replication & A robustness claim for declared routes; not universal memory utility \\
\bottomrule
\end{tabular}
\end{table}

\section{Data Availability}

An anonymized supplementary package is prepared for review. It contains the
public fixture definitions, canonical adapters, analysis code, and sanitized
aggregate receipts needed to reproduce the public cohorts. It excludes raw
agent events, credentials, private transitions, hidden oracles, reference
patches, and user-specific client configuration. The supplementary archive must
be scrubbed of version-control history and author-identifying metadata before
upload; the non-anonymous project release is not used during review.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
