\section{Evaluation Plan}

The primary outcome is task success under a frozen behavioral oracle. Secondary
outcomes include action timing, context and API cost, optional-memory use, and
stale-claim-consistent conflict actions. A conflict action is an observable
action that advances a behavior declared stale for that case and conflicts with
current source or the controller oracle. It is not a claim that memory caused an
agent's internal reasoning error.

Each confirmatory run is independently labeled by two blinded human raters for
secondary action outcomes; disagreement requires an independent adjudicator.
Raters do not see condition or provider identity. Pending or unrateable labels
remain missing rather than becoming zeros.

The primary analysis unit is a case, agent client, and actual model cluster.
Repeated runs and seeds estimate stability inside the cluster. We aggregate
matched repetitions before calculating the primary difference, use a clustered
bootstrap interval, and use a paired cluster sign-flip test. This prevents one
task with many retries from appearing to be many independent engineering
problems.

Each confirmatory family is restricted to one agent and actual-model cohort.
An immutable analysis manifest binds the registry commitment, H1/H2 condition
pairs, power-plan commitments, and every case/repetition/seed row before
outcomes are read. Missing, duplicate, invalid, or unplanned rows fail closed;
additional agent/model cohorts are reported as independent replications rather
than pooled as extra cases.

Before confirmatory outcomes are read, the study freezes an absolute minimum
detectable difference and a nuisance envelope of paired-discordance rates. The
published planning receipt selects the largest required cluster count across
that envelope using exact paired-binary power while assuming repeated runs
within a cluster are perfectly correlated. Thus repetitions receive no
sample-size credit during planning; they characterize stability rather than
inflate the apparent number of engineering problems. The planning calculation
does not replace the final clustered sign-flip analysis. Because H1/H2 use Holm
adjustment, planning uses the conservative Bonferroni threshold for a
two-comparison family rather than claiming unobserved joint Holm power.

The primary paper claim is limited to canonical bounded retrieval on the frozen
transfer corpus: Memorix versus no memory and bounded raw replay form the
Holm-corrected primary family. Mem0 and AgentMemory use the same canonical
surface as secondary baseline comparisons. Budgeted native product behavior is
a separately preregistered product-surface analysis; unrestricted product
experience is exploratory. A confirmatory table will be inserted only after the
preregistered corpus and execution gates are complete.
